### 2023-02-15 notebooks/conformal.qmd
penalties

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using MLJFlux
```

@@

```{julia}
clf = NeuralNetworkClassifier()
```

@@

>>>>

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using Flux
using MLJBase
using MLJFlux
using Plots
```

@@

```{julia}
builder = MLJFlux.@builder Chain(
    Dense(n_in, 32, relu),
    Dense(32, n_out)
)
clf = NeuralNetworkClassifier(builder=builder, epochs=100)
```

@@

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
```
